Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
adding annotation.
Use "correct semantic" instead of "no type error"
Introduction: wording

One of the best features of Haskell is its strong type system, 
which ensures no type errors in programs if they can be complied.
Thanks to this, it is said that programs written in Haskell have less bugs
than other programming languages which do not provide such strong type systems.

@@

Unfortunately, the strong type system of Haskell does not guarantee
no value errors.
Haskellers is, however, apt to rely on the strong type system too much.
They tend to write less test code than programmers of other
programming languages.

@@

TBD: talk about hspec.

@@

TBD: talk about Cabal.

>>>>

Haskell has a very strong type system, which ensures that most type errors are
detected at compile time rather than runtime.  Thanks to this, we assume that
programs written in Haskell have less bugs than programs written in programming
languages that do not provide such a strong type system.

@@

Unfortunately, the strong type system of Haskell does not guarantee correct
semantic.
Haskellers is, however, apt to rely on the strong type system too much.
They tend to write less test code than programmers of other
programming languages.

@@

TBD(@sol): talk about hspec.

@@

TBD(@sol): talk about Cabal.
